Ground state energy of quantum dots using the coupled cluster method

### 2018-04-17 project_2/article/article.tex
Add CCD energy equation

        \subsubsection{Coupled cluster doubles energy equation}
            Using the doubles approximation with the cluster operator $T_2$
            defined in \autoref{eq:T_2} the energy equation becomes
            \begin{align}
                \eccd
                &=
                E_0
                + \bslat e^{-T_2}H_N e^{T_2}\kslat.
            \end{align}
            As the doubles cluster operator doubly excites the reference and
            using the expansion in \autoref{eq:sim_norm_hamiltionian_expansion}
            we see that we can write the energy equation as
            \begin{align}
                \eccd
                &=
                E_0
                + \bslat H_N(1 + T_2)\kslat,
            \end{align}
            as the Hamiltonian is only able to de-excite one pair of single
            particle functions.

@@

        \bslat H\kslat

@@

>>>>

        \subsubsection{Coupled cluster doubles energy equation}
            Using the doubles approximation with the cluster operator $T_2$
            defined in \autoref{eq:T_2} the energy equation becomes
            \begin{align}
                \eccd
                &=
                E_0
                + \bslat e^{-T_2}H_N e^{T_2}\kslat.
            \end{align}
            As the doubles cluster operator doubly excites the reference and
            using the expansion in \autoref{eq:sim_norm_hamiltionian_expansion}
            we see that we can write the energy equation as
            \begin{align}
                \eccd
                &=
                E_0
                + \bslat H_N \kslat + \bslat (H_N T_2)_c\kslat,
            \end{align}
            as the Hamiltonian is only able to de-excite one pair of single
            particle functions. By construction we have that
            \begin{align}
                \bslat H_N \kslat = 0.
            \end{align}
            In the second term only the normal ordered two-body operator can
            contribute as the cluster operator gives a total excitation of $+2$.
            As we are projecting onto the reference we have to de-excite to zero
            again. The normal ordered Fock operator is at most able to excite
            and de-excite by $1$ and does therefore not contribute to the
            overall expression.
            \begin{align}
                \bslat (W_N T_2)_c \kslat
                &= \frac{1}{4}\sum_{ijab}\bra{ij}\ket{ab}t_{ij}^{ab}.
            \end{align}
            In total the energy equation reduces to
            \begin{align}
                \eccd
                &= \sum_{i} h_i^i + \half \sum_{ij}\bra{ij}\ket{ij}
                + \frac{1}{4}\sum_{ijab}\bra{ij}\ket{ab}t_{ij}^{ab},
            \end{align}
            where the first two terms come from the reference energy as shown in
            \autoref{eq:reference_energy}.

@@

        E_0 \equiv \bslat H\kslat

@@

        \label{eq:reference_energy}
